Introduction

### 2015-07-21 dissertation/problems.tex
Excuse bad philosophy

>>>>

Problem~\ref{prob:badphil} has been a growing concern throughout this
work. A proper evaluation should be an important part of the
dissertation, and yet, the problems discussed in
Section~\ref{sec:evalproblems} are so severe that the time frame of
this work does not allow a satisfactory solution to these
problems. The paper discussed in Section~\ref{sec:conphil} serves to
excuse this.
